Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-19 tex/Supplementary Information/PNAS-template-main.tex
补充说明第一节文字部分

% \section*{Supplementary Information Methods}
\section*{Methods S1. Definition of study area}
% 黄河经历了水资源开发利用和制度改革
The study area is the Yellow River Basin (YRB), 
which has experienced the most intense water exploitation 
and the most dramatic reform of management regimes.

@@

\section*{Methods S2. Detailed information on dataset and processing}
Add a materials' subsection if you need to.

@@

%%% Each figure should be on its own page
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../../figures/supplementary_information/sf_measured_runoff.pdf}
\caption{Natural measured runoff of Yellow River within different periods.}
\end{figure}

>>>>

% \section*{Supplementary Information Methods}
\section*{Methods S1. Definition of study area}
% 黄河经历了水资源开发利用和制度改革
The study area is the Yellow River Basin (YRB), which has experienced the most intense water exploitation and the most dramatic shifts of management regime (Supplementary Fig. 1). According to ecological zoning, landscapes types, water resource zoning et al., the Yellow River Basin can be divided into four different regions (supplementary Fig. 2), which has been widely recognized (ref.). Using this division, there are also some differences of nature between different regions regarding water utilization regimes (supplementary Fig. 3):
\begin{itemize}
    \item \textbf{Source Region (SR):} Over 50\% of natural runoff was produced in this region. The most ecology function here is water conservation, as sparsely populated and less economically developed.
    \item \textbf{Upper Region (UR):} With the highest per capita irrigated land area, there are numbers of large irrigation lands in this region. However, because of backward production methods, efficiency of irrigation are used to be very low.
    \item \textbf{Middle Region (MR):} Crossing Loess Plateau, famous rich-sand area, Yellow River loads most of its sediments here with the highest soil erosion risk. To reverse this situation, the grain for green project changed the water utilization here strikingly.
    \item \textbf{Lower Region (LR):} With dense population and the traditional agricultural trajectory, lower region used to be the largest water use region. However, as the industrial transformation going, proportion of agriculture keeps decreasing, but LR is still the largest water use region in each aspect.
\end{itemize}

@@

\section*{Methods S2. Detailed information on dataset and processing}
Since the Yellow River Basin consists of ten provincial areas, the above division can also maintain broad consistency with administrative divisions.
Add a materials' subsection if you need to.

@@

%%% Each figure should be on its own page
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../../figures/placeholder_s}
    \caption{Yellow River Basin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../../figures/supplementary_information/sf_measured_runoff.pdf}
\caption{Natural measured runoff of Yellow River within different periods.}
\end{figure}
